True versus apparent shapes of astrophysical bow shocks

### 2017-02-06 papers/Paper1/sec-conic.tex
Final hand-improvements to Fig 5

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure*}
\setlength\tabcolsep{0pt}
\begin{tabular}{ll}
  (a) & (b) \\
  \includegraphics[height=0.45\linewidth]{figs/ellipse_py}
      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_py}
\end{tabular}
\label{fig:conics}
\caption{Example off-center conic sections that can form quadrics of
  revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
  between the conic section parameters \(a\), \(b\), \(\theta_c\) and
  the bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
  defined in Fig.~\ref{fig:characteristic-radii}. The center of the
  conic is located at a distance $x_0=a \mp R_0$ from the origin along the
  $x$ axis. Where the minus sign on $R_0$ correspond to ellipses and the plus
  sign to hyperbolas}
\end{figure*}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}

>>>>

%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates that the given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary  
\begin{figure*}
\setlength\tabcolsep{2em}
\begin{tabular}{ll}
  (a) & (b) \\
  \includegraphics[height=0.45\linewidth]{figs/ellipse_edited}
      & \includegraphics[height=0.45\linewidth]{figs/hyperbola_edited}
\end{tabular}
\label{fig:conics}
\caption{Example off-center conic sections that can form quadrics of
  revolution: (a) ellipse, (b) hyperbola.  The relationship is shown
  between the conic section parameters \(a\), \(b\), \(\theta_c\) and the
  bowshock characteristic radii \(R_0\), \(R_{90}\), \(R_c\), as
  defined in Fig.~\ref{fig:characteristic-radii}. The origin (center
  of the weaker flow) is indicated by a red star, the center of
  curvature of the apex of the bow shock is indicated by a green dot,
  and the geometric center of the conic section is indicated by a blue
  cross.  }
\end{figure*}
\begin{figure}
\includegraphics[width=\linewidth]{conic1}
\caption{Example of a family of conic sections, all with the same
  radius of curvature at their apex (marked by white dot) on the
  \(x\)~axis: \(R_c = 2 R_0\). The parameter
  $\theta_c = \pm \tan^{-1} b/a$ describes the family, with negative
  values corresponding to hyperbolae.}
\label{fig:conics-family}
\end{figure}
